---
title: "DataFest 2017"
author: "Chapel-Boys.R"
date: "4/1/2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(tibble)
library(ggalt)
```

## Introduction

We seek to use [OUTSIDE_DATA] to predict the propensity to book. In order, to measure such user behavior we consider a number of classification models and then use a validation procedure to select that one that performs most optimally. Then, we attempt to demonstrate the [OUTSIDE_DATA]'s importance to our model and explanatory power. 

## PCA

Evidently, the dest.txt file contains valuable information in relation to characteristics unique to each destination. However, it is prudent to begin our analysis by shrinking the number of explanatory variables from 144 to a smaller number of principal components. 

```{r, include=FALSE}
load(file="dest.RData")
load(file="dest_sub.RData")
apply(dest_sub ,2,mean)
apply(dest_sub, 2, var)
pcaCharts <- function(x) {
    x.var <- x$sdev ^ 2
    x.pvar <- x.var/sum(x.var)
    print("proportions of variance:")
    print(x.pvar)
    
    par(mfrow=c(2,2))
    plot(x.pvar,xlab="Principal component", ylab="Proportion of variance explained", ylim=c(0,1), type='b')
    plot(cumsum(x.pvar),xlab="Principal component", ylab="Cumulative Proportion of variance explained", ylim=c(0,1), type='b')
    screeplot(x)
    screeplot(x,type="l")
    par(mfrow=c(1,1))
}
```

## PC1 & PC2

Hence, we can visualize the first two orthogonal principal components:

```{r, echo = FALSE, dplyr}
dest$srch_destination_latitude <- as.character(dest$srch_destination_latitude)
dest$srch_destination_latitude <- as.numeric(dest$srch_destination_latitude)
dest$srch_destination_longitude <- as.character(dest$srch_destination_longitude)
dest$srch_destination_longitude <- as.numeric(dest$srch_destination_longitude)
dest <- na.omit(dest)
dest_sub <- dest[,-2]
rownames(dest_sub) <- dest_sub[,1]
dest_sub <- dest_sub[,-1]
dest_sub <- dest_sub[,-1]
pca.out=prcomp(dest_sub, scale=TRUE)
pcaCharts(pca.out)
#pca.out
#names(pca.out)
#biplot(pca.out, scale=0)

d <- filter(dest, 
    srch_destination_latitude < -11.876272 &
    srch_destination_longitude < -76.898208 & 
    srch_destination_latitude > -12.109458 &  
    srch_destination_longitude > -77.139983 # Lima, Peru
| srch_destination_latitude < -33.850076 & 
  srch_destination_longitude < 151.223994 & 
  srch_destination_latitude > -33.871849 & 
  srch_destination_longitude >  151.201960 # Sydney, Aus

| srch_destination_latitude < 19.124972 & 
  srch_destination_longitude < 72.930218 & 
  srch_destination_latitude > 19.058467 & 
  srch_destination_longitude >  72.805771 # Mumbai, India
) 

df_pc <- data.frame(pca.out$x, Species = dest$srch_destination_latitude)

df_pc <- rownames_to_column(df_pc, var = "srch_destination_lat")

pca_sub <- filter(df_pc, 
 dest$srch_destination_latitude <= -11.876272 & dest$srch_destination_latitude >= -12.109458
|
dest$srch_destination_latitude  <= 19.124972& dest$srch_destination_latitude >= 19.058467 
| dest$srch_destination_latitude <= -33.850076 & dest$srch_destination_latitude >= -33.871849
)

df_pc_vir <- filter(df_pc, dest$srch_destination_latitude <= -11.876272 & dest$srch_destination_latitude >= -12.109458)  # df for 'virginica'

df_pc_set <- filter(df_pc, dest$srch_destination_latitude <= 19.124972 & dest$srch_destination_latitude >= 19.058467)  # df for 'setosa'#

df_pc_ver <- filter(df_pc, dest$srch_destination_latitude <= -33.850076 & dest$srch_destination_latitude >= -33.871849)  # df for 'versicolor'

ggplot(pca_sub, aes(PC1, PC2, col=Species)) + 
  geom_point(aes(shape=Species), size=2) +
  scale_shape_identity() +   # draw points
  labs(title="Iris Clustering", 
       subtitle="With principal components PC1 and PC2 as X and Y axis",
       caption="Source: Iris") + 
  coord_cartesian(xlim = 1.2 * c(min(pca_sub$PC1), max(pca_sub$PC1)), 
                  ylim = 1.2 * c(min(pca_sub$PC2), max(pca_sub$PC2))) +   # change axis limits
  geom_encircle(data = df_pc_vir, aes(x=PC1, y=PC2)) +   # draw circles
  geom_encircle(data = df_pc_set, aes(x=PC1, y=PC2)) + 
  geom_encircle(data = df_pc_ver, aes(x=PC1, y=PC2))

#pca_select <- 
```

## Lat/Long

```{r, ggplot2}
load(file="int.RData")
df_5 <- df_pc[c("srch_destination_id", "PC1", "PC2", "PC3", "PC4", "PC5")]
int_datasub$srch_destination_id = as.character(int_datasub$srch_destination_id)
int_comb <- left_join(int_datasub, df_5)


```